%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
  \cventry
    {Research Enginner} % Job title
    {ALMAnaCH, Inria} % Organization
    {Paris, France} % Location
    {Mar. 2022 - Current} % Date(s)
    { 
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Researching language models for languages displaying high variability, in particular Arabic dialects used on social media.}
        \item {Implementing new pre-training techniques for french language representation.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Machine Learning Scientist} % Job title
    {Siren Analytics} % Organization
    {Beirut, Lebanon} % Location
    {Jan. 2021 - Feb. 2022} % Date(s)
    { 
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Researched and developed semantic search engines using state-of-the-art NLP and IR approaches.}
        \item {Built an OCR API for ID card scanning.}
        \item {Designed and developed document AI solutions to extract information from scanned documents.}
        \item {Developed a real-time anomaly detection system for lockdown mobility permit.}
        \item {Developed encryption solutions for model IP protection.}
        \item {My work also involved researching and applying latest AI solutions, evaluating software solution vendors, and internship mentoring.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Graduate Research Assistant} % Job title
    {MIND Lab - American University of Beirut} % Organization
    {Beirut, Lebanon} % Location
    {Sep. 2018 - Jan. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Co-founded AUB’s Machine INtelligence Development (MIND) Lab  \hyperlink{sites.aub.edu.lb/mindlab}{\url{https://sites.aub.edu.lb/mindlab}}}
        \item {My research focused on state-of-the-art NLP technologies for natural language processing, generation, and chatbots.}
        \item {Worked on pre-training various Arabic language models that ranges from RNN-based to the Transformer-based models, using Cloud TPU and GPU instances.}
        \item {Researched improving temporal and spacial resolution of remote sensing ML systems for soil moisture prediction.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Graduate Teaching Assistant} % Job title
    {ECE Dept. - American University of Beirut} % Organization
    {Beirut, Lebanon} % Location
    {Feb. 2018 - Jan. 2020} % Date(s)
    { 
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {EECE 435L: Software Tools Lab, Co-Instructor (3 semesters).  Delivered a range of teaching and assessment activities including tutorials directed towards the delivery of modern Software Tools at the undergraduate level.}
        \item {EECE 696: Applied Parallel Programming, Lab instructor (1 semester). Delivered hands-on experience to graduate students on parallel programming and GPU computing using the CUDA C/C++ framework on local computers and on AWS.}
        \item {EECE 330: Data Structures and Algorithms, Lab instructor (1 semester). Delivered hands-on experience on fundamental algorithms and data structures used in software applications at the undergraduate level using C++.}
        \item{Introduced a plagiarism detection tool for computer code to the Electrical Engineering Department.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Reviewer for the following journals:} % Job title
    {Academic Reviewer} % Organization
    {} % Location
    {2020 - Current} % Date(s)
    { 
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Journal of King Saud University - Computer and Information Sciences (IF: 13.47)}
        \item {Expert Systems with Applications (IF: 6.95)}
        \item Workshop on Arabic Natural Language Processing (h-index: 24, i10-index: 51)
        \item Workshop on Open-Source Arabic Corpora and Processing Tools
        \item {ACM Transactions on Asian and Low-Resource Language Information Processing - TALLIP (IF: 1.42)}
        \item {Language Resources and Evaluation Journal (IF: 1.36)}
      \end{cvitems}
    }
    \newline
    \newline
%---------------------------------------------------------
    \cventry
    {AI Instructor} % Job title
    {Zaka} % Organization
    {Online} % Location
    {May. 2020} % Date(s)
    { 
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Gave a 4-part online workshop series titled \textit{A Comprehensive NLP series} that was focused on delivering the major NLP concepts through hands-on coding examples along with the NLP fundamentals theory.} 
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Machine Learning Expert} % Job title
    {Stars of Science} % Organization
    {Doha, Qatar} % Location
    {Feb. 2020 - Apr. 2020} % Date(s)
    { 
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Provided Machine Learning and Artificial Intelligence solutions as part of the support team that helps contestants throughout their Stars of Science journey}
      \end{cvitems}
    }
%---------------------------------------------------------
 \newline
  \newline
  \cventry
    {Intern} % Job title
    {Huawei Technologies (Lebanon) S.A.R.L.} % Organization
    {Beirut, Lebanon} % Location
    {June 2016  - Aug. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Learned about various LTE principles, base station hardware, and Microwave transmissions systems.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
